Untargeted control doc

### 2023-09-26 untargeted/paruntargeted_control.Rmd
Finished annotating Amm pos with rescue feats

if(amendment=="Amm"){
  if(polarity=="pos"){
    rescue_feats <- c("FT3015", "FT1319", "FT1321")
  } else if(polarity=="neg"){

@@

```{r annotate}
all_stans <- read_csv("metadata/all_stans.csv") %>%
  filter(polarity==!!polarity)

pdf(paste0(output_folder, "anno_eics.pdf"), width = 8, height = 4)
all_stans %>%
  filter(compound_type!="Internal Standard") %>%
  mutate(mz=ifelse(compound_name=="Carnitine", mz[which(compound_name=="Threonine betaine?")], mz)) %>%
  group_by(mz) %>%
  summarise(cmpd_lab=paste0(compound_name, " (", mix, ",", rt, ")", collapse = ", ")) %>%
  # head(6) %>%
  pwalk(function(...){
    row_data <- list(...)
    mass_feats <- best_feat_data %>% filter(mzmed%between%pmppm(row_data$mz, 5))
    chosen_eic <- open_dataset("tmzMLs/pqds") %>%
      filter(polarity==!!polarity) %>%
      filter(amendment==!!amendment) %>%
      filter(samp_type=="Poo" | samp_type=="Std") %>%
      filter(mz%between%pmppm(row_data$mz, 5)) %>%
      filter(rt%between%c(2, 20)) %>%
      dplyr::collect()
    gp_plot <- chosen_eic %>%
      left_join(parametadata, by = join_by(filename, samp_type, amendment, polarity)) %>%
      mutate(samp_type=str_extract(filename, "Mix\\d|Deep|Surf|Poo|Blk")) %>%
      filter(!str_detect(filename, "Mat")) %>%
      mutate(plot_facet=ifelse(samp_type%in%c("Mix1", "Mix2"), "Mixes", "Samples")) %>%
      ggplot() +
      geom_line(aes(x=rt, y=int, group=filename, color=samp_type)) +
      facet_wrap(~plot_facet, scales = "free_y", ncol=1) +
      geom_vline(aes(xintercept=rtmed), color="black", data = mass_feats) +
      geom_text(aes(x=rtmed, y=Inf, label=feature), 
                angle=90, hjust=1, vjust=0.5, data = mass_feats) +
      ggtitle(row_data$cmpd_lab) +
      scale_x_continuous(breaks = 2:20) +
      theme_bw() +
      theme(legend.position = c(0.9, 0.8), legend.title = element_blank(),
            axis.title = element_blank())
    print(gp_plot)
  }, .progress = TRUE)
dev.off()
```

>>>>

if(amendment=="Amm"){
  if(polarity=="pos"){
    rescue_feats <- c("FT3015", Allopurinol="FT1319", Hypoxanthine="FT1321",
                      `DMSOP`="FT1688", "Guan from guan"="FT1707", Tyrosine="FT2200",
                      Phosphocholine="FT2228", Trimethyllysine="FT2278",
                      Dexpanthenol="FT2426", Cytidine="FT2792",
                      Mycogly='FT2814', Inosine="FT2960", Guanosine="FT3015")
  } else if(polarity=="neg"){

@@

```{r annotate}
all_stans <- read_csv("metadata/all_stans.csv") %>%
  mutate(polarity=factor(polarity, levels=c("pos", "neg"))) %>%
  arrange(polarity) %>%
  filter(compound_type!="Internal Standard")
# map(c("Amm", "Nit", "GMP", "Arg"), function(amendment_i){
#   all_stans %>%
#       mutate(amendment=amendment_i) %>%
#       select(amendment, polarity, compound_name, mz, rt, date_added, mix) %>%
#       write_csv("untargeted/anno_template.csv", append = TRUE)
# })
# # Gets copy-pasted into the Excel file manual_annotations.xlsx
# # Then run eicscript.R to render the EICs for each standard and fill it in
# # Afterward, use the "rescue_feats" object above to add those that didn't
# # pass QC for shape or SNR back in

manual_anno <- readxl::read_excel("untargeted/manual_annotations.xlsx")

manual_anno %>% filter(str_detect(notes, "Unpicked"))
```
